Supplementary Material for Cloudbreak

### 2013-06-28 manuscript/nm_supp.tex
update algo description on multiple mappings

The alignment job uses sensitive mapping tools and settings to discover as many mapping locations for each read pair as possible. Given a set of read pairs, each of which consists of a read pair identifier $rpid$ and two sets of sequence and quality scores $<s,q>$, each mapper aligns each pair end set $<s,q>$ in single ended mode and emits the possible locations under the $rpid$ key. Reducers then collect the alignments for each paired end, making them available under one key for the next job. Our implementation contains wrappers to execute the aligners GEM \autocite{MarcoSola:2012hm}, Novoalign\footnote{\url{http://wwww.novocraft.com}}, RazerS 3 \autocite{Weese:2012by}, mrFAST \autocite{Alkan:2009cr}, and Bowtie 2 \autocite{Langmead:2012jh}, as well as the ability to import a pre-aligned BAM file directly to HDFS.

>>>>

The alignment job uses sensitive mapping tools and settings to discover mapping locations for each read pair. Aligners can be executed to report multiple possible mapings for each read, or only the best possible mapping. Given a set of read pairs, each of which consists of a read pair identifier $rpid$ and two sets of sequence and quality scores $<s,q>$, each mapper aligns each pair end set $<s,q>$ in either single- or paired end mode and emits the possible locations under the $rpid$ key. Reducers then collect the alignments for each paired end, making them available under one key for the next job. Our implementation contains wrappers to execute the aligners BWA, GEM \autocite{MarcoSola:2012hm}, Novoalign\footnote{\url{http://wwww.novocraft.com}}, RazerS 3 \autocite{Weese:2012by}, mrFAST \autocite{Alkan:2009cr}, and Bowtie 2 \autocite{Langmead:2012jh}, as well as the ability to import a pre-aligned BAM file directly to HDFS.
